\documentclass[letterpaper]{article}

\usepackage[natbib=true,sorting=ydnt,backend=bibtex,maxcitenames=6]{biblatex}
\addbibresource{citations.bib}
\usepackage{eurosym}
\usepackage{hyperref}
\hypersetup{pdftitle={CristinaLoisResume},
  colorlinks=true,
  linkcolor=blue,
  citecolor=blue,
  urlcolor=blue,
  pdfsubject={Cristina Lois Resume},
  pdfauthor={Cristina Lois},
  pdfpagemode={None},
  pdfstartview=FitH
}

\setlength{\parskip}{1ex}
\setlength{\parindent}{0cm}
\setlength{\oddsidemargin}{1cm}
\setlength{\evensidemargin}{1cm}
\setlength{\topmargin}{-1.0cm}
\setlength{\textwidth}{15cm}
\setlength{\textheight}{22cm}

%\pagestyle{empty}

\setlength{\unitlength}{1cm}

% Horizontal line
\def\hlinha#1{
	\\[-1ex]
	\begin{picture}(#1,0)
%	\thicklines
	\put(0,0){\line(1,0){#1}}
	\end{picture}
}

% Big horizontal line
\def\blinha{\hlinha{17.8}}

% Algunhas definicions
\def\bloque#1{\vspace{.0cm}\begin{large} \textbf{#1}\end{large} \blinha}
%\def\bloque#1{\vspace{.5cm}\begin{large} \textbf{#1}\end{large} \blinha}

\def\nome#1{\begin{center} \begin{Large}\textbf{#1}\end{Large}\end{center}\vspace{0.3cm}}
\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins


\begin{document}

%\nome{\textsc{Cristina Lois}}
\nome{\textsc{Cristina Lois G\'omez}}

% includes postal address
\begin{minipage}[t]{0.6\textwidth}

\hspace*{1.3cm} Athinoula A. Martinos Center for Biomedical Imaging \\
\hspace*{1.3cm} MGH \& Harvard Medical School \\
\hspace*{1.3cm} Building 149 Room 5022 \\
\hspace*{1.3cm} Charlestown MA, 02129  \\
\end{minipage}
\hfill
\begin{minipage}[t]{0.32\textwidth}
    \vfill
\raggedright phone: (617)-319-3615 \\
\raggedright email: \href{mailto:clois@mit.edu}{\texttt{clois@mit.edu}}\\
\raggedright web: \href{http://bit.ly/crislois}{\texttt{bit.ly/crislois}}\\
\end{minipage}

%%\begin{description}
%\vspace*{-0.6cm}
%\begin{center}
%%\hspace*{2.5cm}
%\end{center}
%%\end{description}

\vspace{.5cm}\
\bloque{Academic positions}

\begin{description}

\item[] \textbf{Harvard Medical School \& Massachusetts General Hospital } \hfill Boston, MA\\
Research Fellow in Radiology \hfill \textit{Jul. 2015--present} 
\vspace*{-0.2cm}
\begin{itemize}
%\vspace*{-3.0ex}
 \item Responsible of PET/MR imaging analysis in a clinical study to search for markers of disease and progression in Huntington's Disease. %This is being used in a clinical trial to test new treatments.
 \item Using PET/MR neuroimaging to explore and develop new concepts in healthy and diseased brain function.
 \item Collaborating with a multi-disciplinary team of radiochemists, neuroscientists, and clinical physicians.
  
\end{itemize}

\item[] \textbf{Massachusetts Institute of Technology} \hfill Cambridge, MA \\
``M+Vision'' Research Fellow in Translational Biomedical Imaging \hfill \textit{Jul. 2012--June 2015} 
\vspace*{-0.2cm}
\begin{itemize} 
\item Intensive training on identifying unmet clinical needs and designing
    solutions with high translational potential and marketability.
 \item Conducted interviews with key opinion leaders in oncology, neurology, psychiatry, and radiology.
 \item Responsible of PET/MR imaging in a clinical study to investigate the biological basis of the placebo effect in depression.
\item Built and co-managed an international team of radiochemists, biologists, engineers, and physicians, working on the development of a new PET tracer for early assessment of treatment response in melanoma patients. 
\item Received \$414K in internal grant funding. 
\item Co-organized and taught a MIT IAP course on Biomedical Imaging.
\end{itemize}

\item[]
    \textbf{Hospital Clinic Barcelona} \hfill Barcelona, Spain 
\\
Postdoctoral Research Associate \hfill  \textit{Jan. 2012-- Jun. 2012}
\vspace*{-0.2cm}
\begin{itemize}
\item Evaluated the value of dual-time-point PET for prediction of treatment response in lung
cancer patients.
\end{itemize}

\item[] \textbf{Imaging Science Institute of T\"ubingen} \hfill T\"ubingen, Germany \\
Visiting Scientist \hfill  \textit{Feb. 2011-- Jul. 2011} 
\vspace*{-0.2cm}
\begin{itemize}
\item Analyzed the effect of MRI contrast agents on PET quantification for PET/MRI
applications and demonstrated how to avoid potential artifacts that could impact clinical decisions.
\item Evaluated artifacts caused by dental implants in PET/CT and PET/MR imaging.
\item Worked in a highly collaborative multi-disciplinary team of physicians, MR and PET physicists, and computer engineers.  
\end{itemize}

\item[]
    \textbf{Hospital Clinic Barcelona} \hfill Barcelona, Spain \\
Visiting Researcher \hfill  \textit{3 months in 2009 and 2010} 
\begin{itemize}
\item Compared the performance of GATE \& PeneloPET in simulating a microPET
scanner.
\end{itemize}

\item[] \textbf{University of Santiago de Compostela} \hfill Santiago de Compostela, Spain\\
    ``\'Angeles Alvari\~no'' Fellow \hfill \textit{Dec. 2008--Dec 2011}
    \vspace*{-0.2cm}
   \begin{itemize} 
   \item Designed and built an affordable preclinical SPECT system by reusing a clinical gamma-camera. 
    \item Received 60K \euro~in competitive, public grant funding as PI. 
    \item Led a multi-disciplinary team of physicists, nuclear medicine physicians, and mechanical engineers.
    \item Trained and supervised a graduate student and a postdoc. 
    \item Responsible of designing and teaching one undergraduate laboratory course and two graduate courses.  
   \end{itemize} 
 %  \newpage

\item[] \textbf{University of Tennessee Medical Center} \hfill Knoxville, TN \\
Postdoctoral Research Associate \hfill \textit{Feb. 2007-- Jul. 2008} 
 \vspace*{-0.2cm}
 \begin{itemize} 
 \item Working in collaboration with Siemens, demonstrated the benefits of incorporating time-of-flight information in PET/CT by carrying out a study on a large population of 100 oncology patients. 
\item Published two highly cited papers, one chosen as cover in \textit{Journal of Nuclear Medicine}.
 \end{itemize} 
 
\item[] \textbf{University of Santiago de Compostela} \hfill Santiago de Compostela, Spain\\
    Postdoctoral Research Assistant \hfill \textit{Sep. 2006--Jan 2007}
\vspace*{-0.2cm}
\begin{itemize}
  \item  Measured the neutron fluency in a linear accelerator to estimate its
    contribution to the radiation dose in radiotherapy patients.
 \end{itemize} 

\item[] \textbf{University of Z\"urich} \hfill Z\"urich, Switzerland \\
 \&
\item[] \vspace*{-2.5ex} \textbf{University of Santiago de Compostela} \hfill Santiago de Compostela, Spain\\
    Research \& Teaching Assistant \hfill \textit{Sep. 2001--Jun. 2006}
\vspace*{-0.2cm}
\begin{itemize}
\item   Contributed to the design and development and carried out performance studies of the silicon microstrip detectors installed in the Silicon Tracker of the LHCb experiment at CERN.
\item Trained and supervised undergraduate students. 
\end{itemize} 
\end{description}



\bloque{Awards}

\begin{description}

\item[] M+Vision Advanced Fellowship (declined), Madrid-MIT M+Vision Consortium  \hfill \textit{Aug. 2013}

\item[] M+Vision Fellowship\\
Madrid-MIT M+Vision Consortium \hfill \textit{Jul. 2012} 

    Ranked 2nd among more than 100 applicants.
\item[] ``Best Oral Presentation in Nuclear Medicine''\\
    Spanish Nuclear Society Annual Meeting \hfill\textit{Oct. 2010}

\item[] Front cover of the Journal of Nuclear Medicine, Vol. 50 \hfill \textit{Aug. 2009} \\
    Featuring results on ``Impact of Time-of-Flight on PET Tumor Detection''.

\item[] Jos\'e Castillejo Fellowship\\
Ministerio de Educaci\'on y Ciencia, Spain \hfill \textit{Sep. 2007--Jun. 2008}

\item[] \'Angeles Alvari\~no Fellowship\\
    Xunta de Galicia, Spain \hfill \textit{Dec. 2008--Dec. 2011}

    Ranked 2nd among more than 200 applicants.

\item[] Predoctoral research grant\\
    Universidad de Santiago de Compostela, Spain \hfill 
    \textit{ Oct. 2005--May 2006}\\
    Excma. Diputaci\'on Provincial de A Coru\~na, Spain \hfill 
    \textit{Jul. 2003--Jul. 2004}\\
	Excma. Diputaci\'on Provincial de A Coru\~na, Spain \hfill
    \textit{Jul. 2002--Jul. 2003}\\

\end{description}

\bloque{Grants}

\begin{description}
\item 
Treatment response in advanced melanoma patients\\
{\it Funding Agency: } Madrid-MIT M+Vision Consortium.\\
{\it Duration: } Feb. 2013--Dec. 2014.\\ 
{\it Budget: } \$414,473.\\
{\it Principal Investigators: } Osasere Evboumwan and Cristina Lois.\\

\item

Development of a pinhole SPECT system based on a conventional gamma camera \\
{\it Funding Agency: }  Xunta de Galicia, Spain.\\
{\it Duration: } Dec. 2009--Dec. 2011.\\ 
{\it Budget: } 60000 \euro.\\
{\it Principal Investigator: } Cristina Lois.\\

\item

Development and evaluation of the next generation of high-performance PET Scanners   \\
{\it Funding Agency:} Programa Jos\'e Castillejo, Ministerio de Educaci\'on y
Ciencia.\\
{\it Duration:} Jul. 2007--Jun. 2008.\\ 
{\it Budget:} 25000 \euro.\\
{\it Principal Investigator:} Cristina Lois.\\

\end{description}

\bloque{Education}

\begin{description}
    \item[] \textbf{PhD in Physics}, with European Doctorate \hfill
        \textit{Oct. 2001 - May 2006}\\
    University of Santiago de Compostela \hfill Santiago de
    Compostela, Spain 
    \item[] \textbf{MSc in Particle Physics \& Non-linear Dynamics} \hfill \textit{Oct. 2001 - Sep. 2003}
        \\
    University of Santiago de Compostela \hfill Santiago de
    Compostela, Spain 
    \item[] \textbf{BSc in Physics} \hfill \textit{Oct. 1995 - Sept. 2001} \\
    University of Santiago de Compostela \hfill Santiago de
    Compostela, Spain
   \end{description} 


\bloque{Publications}

\textit{See also my Google Scholar profile at}
\href{http://bit.ly/cloispubs}{\texttt{bit.ly/cloispubs}}.

%\input{citations.tex}
\nocite{*}

\begingroup
\renewcommand{\section}[2]{}%
\printbibliography
%\bibliographystyle{cv}
%\bibliography{citations}
\endgroup

    \newpage
    
\bloque{Teaching}

\begin{description}
\item[] \textbf{Massachusetts Institute of Technology} \hfill Cambridge, MA

    \href{http://student.mit.edu/searchiap/iap-9289af8d497571ef0149811f01ff0052.html}
    {``An introduction to biomedical imaging''} (IAP) \hfill \textit{Jan. 2015}

\item[] \textbf{Hospital Cl\'{\i}nic de Barcelona} \hfill Spain
    \begin{itemize}
        \item ``IX Course on Instrumentation and Quality Control in Nuclear
                Medicine'' \hfill\textit{Nov. 2013} 
        \item ``VIII Course on Instrumentation and Quality Control in Nuclear
                Medicine'' \hfill\textit{Nov. 2011} 
    \end{itemize}

\item[] 
    \textbf{University of Santiago de Compostela} \hfill Santiago de
    Compostela, Spain
    \begin{itemize}
        \item ``Physics II'' (BSc in Chemistry)
            \hfill\textit{2010 \& 2011} 
        \item ``Medical Applications of Ionizing Radiation'' (Ms in Physics) 
            \hfill\textit{2009 \& 2010} 
        \item ``Technological Applications of Ionizing Radiation'' (Ms in Physics)
            \hfill\textit{2010 \& 2011} 
    \end{itemize}

\end{description} 
    
\bloque{Professional service}

\begin{description}
\item Chair of the `` PET imaging'' session at the 2011 IEEE Nuclear Science Symposium and Medical Imaging Conference, Valencia, Spain.

\item Referee for  {\em Medical Physics}, {\em Physics in Medicine and Biology}, and {\em Zeitschrift f\"ur Medizinische Physik}.

\item  Management Committee Member to \href{http://www.pet-mri.eu}{EU COST
    Action TD1007} for "Bimodal PET-MRI molecular imaging technologies and applications for in vivo monitoring of disease and biological processes".
    
\item Reviewer for the Instituto de Salud Carlos III Grants 2015, in the modality of Technological Developments for Health Applications (AES 2015).

\end{description}

\bloque{Professional licenses}

\begin{description}

\item Radioactive Facilities Supervisor License, Spanish Nuclear Safety Council, 2009.  

\end{description}

\end{document}
